# Investigating Grain Size Variance

First, we will look at a boxplot of the distributions of the median grain size 
for all debris flow fans broken down by lithology.

```{r load, echo = FALSE, warning=FALSE, message=FALSE, results=FALSE}

library(tidyverse)
library(DBI)
library(ggplot2)
library(patchwork)
library(ggridges)


volume <- read_csv("C:/Users/saraw/Box Sync/MS_Research/Processed_Data/summary_data-sets/final_datasets/DF_Volume_data-set.csv")

GSD<- read_csv("C:/Users/saraw/Box Sync/MS_Research/Processed_Data/summary_data-sets/final_datasets/GSD_Summary_Data.csv")


```

Plotting boxplot of median grain size:

```{r boxplot}

GSD %>% 
  filter(complete.cases(subD50),
         (Lith_type == "igneous" | Lith_type == "sedimentary")) %>% 
  mutate(subD50_phi = log2(subD50)) %>% 
  relocate(subD50_phi, .after = subD50) %>% 
  ggplot(aes(x = Lith_type, y= subD50_phi, color = Lith_type))+
  geom_boxplot() +
  geom_jitter(alpha = 0.5) +
  labs(y = "Subsurface D50 (phi)", x = "", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom")


```

It is surpising that there is not much of a discernible difference in median
grain size distributions between the sedimentary and igneous rocks.


Density plot of median grain size by lithology:


```{r density plot, warning=FALSE, message=FALSE}

GSD %>% 
  filter(
         (Lith_type == "igneous" | Lith_type == "sedimentary")) %>% 
  mutate(subD50_phi = log2(subD50),
         surD50_phi = log2(surD50)) %>%
  ggplot(aes(x = subD50_phi, y = Lith_type, fill = Lith_type)) +
  geom_density_ridges(scale = 8) +
  theme_minimal() +
  labs(y = "", x = "D50") +
  theme(legend.position = "none")

```

We can see that the igneous distribution is narrower than that of the sedimentary rocks. 

