# Subsurface vs Surface Grain Size Distribution


```{r load2, echo = FALSE, warning=FALSE, message=FALSE, results=FALSE}

library(tidyverse)
library(DBI)
library(ggplot2)
library(patchwork)
library(ggridges)


volume <- read_csv("C:/Users/saraw/Box Sync/MS_Research/Processed_Data/summary_data-sets/final_datasets/DF_Volume_data-set.csv")

GSD<- read_csv("C:/Users/saraw/Box Sync/MS_Research/Processed_Data/summary_data-sets/final_datasets/GSD_Summary_Data.csv")


```


Scatter plot of the surface vs subsurface median grain size
```{r scatterplot, warning=FALSE}

GSD %>% 
  filter(complete.cases(subD50),
         (Lith_type == "igneous" | Lith_type == "sedimentary")) %>%
  mutate(subD50_phi = log2(subD50),
         surD50_phi = log2(surD50)) %>% 
  ggplot(aes(x = subD50_phi, y = surD50_phi, color = Lith_type))+
  geom_abline(aes(slope = 1, intercept = 0),  
              size = 0.5) +
  geom_point(size = 4) +
  guides(color = guide_legend(), size = guide_legend()) +
  theme_minimal() +
  labs(x = "Subsurface D50 (phi)", y = "Surface D50 (phi)", 
       color = "Lithology") +
  theme(legend.position = "bottom")

```

The line in the plot represents the 1 to 1. The data would follow the line if
the subsurface and surface distributions were the same. However, majority of
the points are on the left of the line, indicating that the surface distribution 
is coarser than the subsurface distribution. 